---
title: "Midterm Instructions: Concepts"
author: "Yonatan Amzaleg"
date: "10/4/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the first R Markdown for the midterm assignment.  It is provided as 3 different markdowns to insure that one question does not prevent anyone from completing other parts of the exam.  Please edit the markdown such by either (1) striking *italicized* words that are incorrect using ~~strikethrough~~ (\~\~strikethrough\~\~), (2) deleting the incorrect *italicized* terms, or (3) putting the correct answer where requested.

See below for an example.  We see that both _true_ and _false_ are options.  To answer the question, we delete _false_

## Example

**Before the exam**

* It is __true__ __false__ that the earth is round and the average temperature of the earth has risen within our lifetime

**After you edited by deleting __false__ or crossing it out, any one of these is ok **

* It is __true__ that the earth is round and the average temperature of the earth has risen within our lifetime
* It is __true__ ~~_false_~~ that the earth is round and the average temperature of the earth has risen within our lifetime

***

## Types of data (any language): 10 points

* "2" is a __String__ datatype.
* 2 is an __Integer__ datatype.
* 2.05 is a __Float__ datatype.
* 2.0 is a __Float__ datatype.
* "" is a __Null__ datatype.
* "true" is a __String__ datatype.
* TRUE is a __Boolean__ datatype.

## Types of data (R): 10 points

* When we run the command *a<-c("d",1,"b")* in *R*, creates a __list__ stored in *a*.

* After we create a variable *a* and fill it with data using the command a<-c("d",1,"b"), we can subset to *d<-a[2]*.  The type of data found in *d* is of type __integer__ .

If you were to load in the diamonds dataset from the ggplot2 library, what type of data is found within diamonds$carat?

>
__float datatype__ 

## Data (these are generalizable file formats, and not specific to R)

* csv files are typically __comma__ deliminited

* The data below is typically __json__

> data ={
        name: "John",
        address: {
            street: "459 E Jon St.",
            city: "Springfield,
            state: "Illinois",
        },
        age:14
    }

* In the example above, data.age is  __Integer__ data-type

* In the example above, data.address is an __unordered__ embedded document (or list)

## Licenses (10 Points)

* It is __True__, If I publish my code working at my new company as MIT License, I can utilize that code
at my next job as part of their projects provided I acknowledge the prior copyrights.

* It is __True__, I can include code R that is GNU GPLv3 within my code  provided I cite the prior copyrights.

* It is __True__, I didn't put a license file in my code but I posted it on github while working in a research laboratory. Because of my lack of thoroughness, I can never use that code again should I take another job, and if I do I could be held liable.  

***


<!-- The text below is just to reformat the page, using css styling -->
```{r results="asis", echo = FALSE}
cat("
<style>
h1 {
    background-color: #990000;
    color:#FFF;
    text-align:center;
}
h2 {
   background-color:#f3d6d6;
   text-align:center;
   color:#333
}
h3 {
   margin-left:-5px;
   color:#333
}

</style>
")
```
